---
title: "hana Meet data exploration "
resource_files:
- inc/Meet_data.RData
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: readable
    logo: inc/hana_logo_small.png
    css: inc/corp-styles.css
    includes:
      before_body: 'inc/google-analytics.js'
---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(plotly)
library(scales)
library(here)
library(rlang)
library(RColorBrewer)  
library(DT)
library(lubridate)
library(RiHana)


load('inc/Meet_data.RData')

hour_blocks<-get_week_hour_blocks()

get_biz_days<-function(start_date,end_date){
  
df <- data.frame(date = seq(start_date, end_date, by = "days"))

days <- df %>% 
  mutate(day = wday(date,week_start=1)) %>%
  filter(day<=5) %>%
  nrow()

days
  
}


```

```{r}

updatedMeetData <- reactive({
  meet_data <-meet_bookings_edited %>% 
    filter(meeting_date>=input$MeetTimeRange[1],
           meeting_date<=input$MeetTimeRange[2],
           grepl(input$hanaLocation,hana_location,ignore.case = TRUE),
           grepl(input$roomType,room_size,ignore.case = TRUE),
           grepl(input$meetingRoom,name),
           grepl(input$FirstBooking,booking_number),
           grepl(input$InternalUsers,employee_related),
           grepl(input$ZeroPriceMeetings,zero_price_res),
           grepl(input$DiscountLevel,discount_level,ignore.case = TRUE),
           grepl(input$memberProduct,member_product,ignore.case = TRUE)) %>% 
#    mutate(resourceid=as.character(resourceid)) %>% 
    inner_join(RiHana::get_hana_meeting_rooms(),by=c("resourceid"="resourceid"))

  return(meet_data)
})


updatedMeetDataSummary <- reactive({
  meet_data <-meet_bookings_edited %>% 
    filter(meeting_date>=input$MeetTimeRange[1],
           meeting_date<=input$MeetTimeRange[2],
           grepl(input$hanaLocation,hana_location,ignore.case = TRUE),
           grepl(input$roomType,room_size,ignore.case = TRUE),
           grepl(input$meetingRoom,name),
           grepl(input$FirstBooking,booking_number),
           grepl(input$InternalUsers,employee_related),
           grepl(input$ZeroPriceMeetings,zero_price_res),    
           grepl(input$DiscountLevel,discount_level,ignore.case = TRUE),
           grepl(input$memberProduct,member_product,ignore.case = TRUE)) %>% 
    summarise(meetings=n(),
              avgPrice=scales::dollar(mean(gross_price,na.rm=TRUE)),
              avgProfit=scales::dollar(mean(gross_price+discount,na.rm = TRUE)),
              avgDiscount=scales::percent(sum(discount,na.rm=TRUE)/sum(gross_price,na.rm=TRUE)))

  return(meet_data)
})


updatedMeetHeatMap<-reactive({
  

  bookings_bin<-meet_bookings_edited %>%
    filter(meeting_date>=input$MeetTimeRange[1],
           meeting_date<=input$MeetTimeRange[2],
           grepl(input$hanaLocation,hana_location,ignore.case = TRUE),
           grepl(input$roomType,room_size,ignore.case = TRUE),
           grepl(input$meetingRoom,name),
           grepl(input$FirstBooking,booking_number),
           grepl(input$InternalUsers,employee_related),
           grepl(input$ZeroPriceMeetings,zero_price_res),
           grepl(input$DiscountLevel,discount_level,ignore.case = TRUE),
           grepl(input$memberProduct,member_product)) %>%
    select(booking_id,meet_day,meet_start,meet_end) %>%
    fuzzyjoin::fuzzy_inner_join(.,hour_blocks,by=c("meet_start"="Hours","meet_end"="Hours"),match_fun=list(`<=`,`>=`)) %>%
    group_by(meet_day,Hours) %>%
    summarise(events=n())

    # bookings_bin_filter<-bookings_bin %>%
    #        filter(meeting_date>=input$MeetTimeRange[1],
    #         meeting_date<=input$MeetTimeRange[2],
    #         grepl(input$hanaLocation,hana_location,ignore.case = TRUE),
    #         grepl(input$roomType,resource_type,ignore.case = TRUE),
    #         grepl(input$meetingRoom,resourcename),
    #         grepl(input$FirstBooking,booking_number),
    #         grepl(input$InternalUsers,employee_related),
    #         grepl(input$ZeroPriceMeetings,zero_price_res),
    #         grepl(input$memberProduct,member_product)) %>%
    #   select(booking_id,meet_day,meet_start,meet_end,Hours) %>%
    #   group_by(meet_day,Hours) %>%
    #   summarise(events=n())

    return(bookings_bin)
  
})

updatedMeetUtilization <- reactive({
  meet_data <-meet_bookings_edited %>% 
    filter(meeting_date>=input$MeetTimeRange[1],
           meeting_date<=input$MeetTimeRange[2],
           grepl(input$hanaLocation,hana_location,ignore.case = TRUE),
           grepl(input$roomType,room_size,ignore.case = TRUE),
           grepl(input$meetingRoom,name),
           grepl(input$FirstBooking,booking_number),
           grepl(input$InternalUsers,employee_related),
           grepl(input$ZeroPriceMeetings,zero_price_res),
           grepl(input$DiscountLevel,discount_level,ignore.case = TRUE),
           grepl(input$memberProduct,member_product)) %>% 
    summarise(utilized_hours=as.numeric(sum(meeting_length),units="hours"))
  
  
biz_days<-get_biz_days(input$MeetTimeRange[1],input$MeetTimeRange[2])

meet_rooms<-RiHana::get_hana_meeting_rooms() %>% 
  filter(grepl(input$hanaLocation,hana_unit,ignore.case = TRUE),
           grepl(input$roomType,current_room_size,ignore.case = TRUE),
           grepl(input$meetingRoom,room_name)) %>% 
  summarise(rooms=n_distinct(room_name))

utilization<-scales::percent(meet_data$utilized_hours/(meet_rooms$rooms*biz_days*10))

return(utilization)

})


```

Sidebar {.sidebar}
=====================================
###### **Data Updated:** _`r as_date(file.info('inc/Meet_data.RData')$mtime)` ._

```{r}

dateRangeInput('MeetTimeRange',
      label = 'Choose the time range',
      min= RiHana::get_relevant_date()$yoy_date,
      max= RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$ytd_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )

selectInput("hanaLocation", label = "Choose the location",
           choices = c("All" = "*",
                        "Park District" = "Park District",
                        "Park Place" = "Park Place"),
            selected= c("All"),
            multiple = FALSE)

selectInput("roomType", label = "Choose room type",
            choices = c("All" ="*",
                        "Large" = "Large",
                        "Medium" = "Medium",
                        "Small" = "Small"), 
            selected = c("All"),
            multiple = FALSE)

selectInput("memberProduct", label = "Choose the user's product",
           choices = c("All" = "*",
                        "Team" = "Team",
                        "Share" = "Share",
                        "Meet" = "Meet",
                        "Member" = "Team|Share"),
            selected= c("All"),
            multiple = FALSE)
helpText("Note: 'Member' refers to users who are either Team or Share members")

selectInput("DiscountLevel",label="Filter for level of discount",
             choices=c("All"="*",
                       "Full"="full",
                       "Partial"="partial",
                       "None"="none"),
             selected="*",
            multiple = FALSE)

selectizeInput(
        'meetingRoom', 'Choose a Room', choices = unique(meet_bookings_edited$name),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        )
)

radioButtons("ZeroPriceMeetings",label="Remove zero priced bookings",
             choices=c("No"="*",
                       "Yes"="^0$"),
             selected="*",)
helpText("Note: Zero Price meetings are meetings that have a $0 gross price")


radioButtons("FirstBooking",label="Member First Booking",
             choices=c("No"="*",
                       "Yes"="^1$"),
             selected="*")


radioButtons("InternalUsers",label="Remove Internal Users",
             choices=c("No"="*",
                       "Yes"="^0$"),
             selected="*")

             
```

<strong>Booking Lead time</strong> - Time (in hours) from meeting creating until meeting start time

<strong>Meeting Length</strong> - Length of reservation (in minutes)

<strong>First Booking</strong> - Filter for only first reservations of members.

<strong>Internal Users</strong> - Filter out Hana and CBRE users.

Meet {data-orientation=rows}
===================================== 


Row{ width=8}
-------------------------------------
### Meet Bookings

```{r}
my_colors<-hana_color_palette(3)

renderValueBox({
  meetSummary<-updatedMeetDataSummary()
valueBox(prettyNum(meetSummary$meetings,big.mark = ","), 
         icon = "fa-calendar-o",
         color = "#E6E2DA")
})
```

### Average Gross Price

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  meetSummary<-updatedMeetDataSummary()
valueBox(prettyNum(meetSummary$avgPrice,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#E6E2DA")
})

```

### Average Net Price

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  meetSummary<-updatedMeetDataSummary()
valueBox(prettyNum(meetSummary$avgProfit,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#E6E2DA")
})
```


### Average Discount(%)

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  meetSummary<-updatedMeetDataSummary()
valueBox(prettyNum(meetSummary$avgDiscount,big.mark = ","), 
         icon = "fa-percentage",
         color = "#E6E2DA")
})
```


### Usage Rate

```{r}
my_colors<-hana_color_palette(3)
renderValueBox({
  meetUtilization<-updatedMeetUtilization()
valueBox(prettyNum(meetUtilization,big.mark = ","), 
         icon = "fa-cog",
         color = "#E6E2DA")
})
```


Row
-------------------------------------

### Meet Heatmap 

```{r }

# renderPlotly({
# 
#   bookings_bin<-updatedMeetHeatMap()
#   plot_ly(bookings_bin,x = ~Hours, 
#           y = ~meet_day,
#           z = ~events, 
#           colors = colorRamp(c("yellow", "red")), 
#           type = "heatmap") %>% 
#     layout(xaxis = list(title = 'Hour of day'),
#          yaxis = list(title = 'Day of week'))
# 
#     
# 
# })   

renderPlotly({
  bookings_bin<-updatedMeetHeatMap()
  p<-ggplot(bookings_bin, aes(x=Hours,y=meet_day))+
  geom_tile(aes(fill=events))+
  scale_fill_gradientn(colours=brewer.pal(9,"YlOrRd"),
                       breaks=seq(0,max(bookings_bin$events),by=2))+
  labs(x="Hour of Day", y="Day of Week")+
  hana_fte_theme()+
  theme(panel.background=element_rect(fill="white", color="white")) +
  theme(plot.background=element_rect(fill="white", color="white")) +
  theme(panel.border=element_rect(color="white")) +
  coord_fixed()

ggplotly(p)

})

```


### Meet Resource Usage

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>%
    group_by(room_size) %>%
    summarise(bookings=n()) %>%
    arrange(bookings) %>%
    mutate(room_size=forcats::as_factor(as.character(room_size))) %>%
    plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~room_size,
          x = ~bookings,
          bargroupgap=0.1,
          bargap = 0.15,
          type="bar")
})

```

Row
-------------------------------------

### Meeting Length

```{r }
renderPlotly({
  meet_data_detail<-updatedMeetData()
  meet_data_detail%>%
  arrange(meeting_length) %>%
  mutate(meeting_length=forcats::as_factor(as.character(meeting_length))) %>%
plot_ly(x = ~meeting_length,
        marker = list(color = "#002D36"),
#        color = ~hana_location,
#        colors = hana_color_palette(n_distinct(meet_data_detail$hana_location),2),
        type = "histogram") %>%
    layout(legend = list(orientation = 'h'),
           xaxis = list(title = 'Length of meeting (minutes)'),
         yaxis = list(title = '# Meetings'))
})


```

### Meet booking lead-time

```{r }

renderPlotly({

meet_data_detail<-updatedMeetData()
  
density <- density(as.numeric(meet_data_detail$booking_lead_time))
plot_ly(x = ~density$x, 
        y = ~density$y, 
        type = 'scatter', 
        mode = 'lines', 
        fill = 'tozeroy',
        fillcolor = '#002D36',
        line = list(width = 0.5)) %>%
  layout(xaxis = list(title = 'Lead Time (hours)',
                      showgrid=F),
         yaxis = list(title = 'Relative Probability'))
})

```


### Meet net price distribution

```{r }

renderPlotly({

meet_data_detail<-updatedMeetData() %>% 
  filter(!is.na(net_price))
density <- density(as.numeric(meet_data_detail$net_price))
plot_ly(x = ~density$x, 
        y = ~density$y, 
        fillcolor = '#002D36',
        line = list(width = 0.5),
        type = 'scatter', 
        mode = 'lines', 
        fill = 'tozeroy') %>%
  layout(xaxis = list(title = 'Net Price',
                      showgrid=F),
         yaxis = list(title = 'Relative Probability'))
})


  


```

Meet Customers 
===================================== 

Column {data-width=700}
-------------------------------------

### Reservations by Customer

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>% 
    group_by(company) %>% 
    summarise(bookings=n()) %>% 
    arrange(bookings) %>% 
    mutate(company=forcats::as_factor(as.character(company))) %>%
    plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~company,
          x = ~bookings,
          bargroupgap=0.1,
          bargap = 0.15,
          type="bar")
})   



```

Column {data-width=300}
-------------------------------------

### Internal vs External Usage

```{r }

renderPlotly({
meet_data_detail<-updatedMeetData() %>% 
  group_by(internal_booking) %>% 
  summarise(bookings=n())
plot_ly(meet_data_detail, 
        labels = ~internal_booking, 
        values = ~bookings, 
        type = 'pie',
        marker = list(colors = hana_color_palette(n_distinct(meet_data_detail$bookings),2),
                      line = list(color = '#FFFFFF', width = 1))) %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
})

```

### Meetings by Member Type

```{r }

renderPlotly({
meet_data_detail<-updatedMeetData() %>% 
  group_by(member_product) %>% 
  summarise(bookings=n())

plot_ly(meet_data_detail, 
        labels = ~member_product, 
        values = ~bookings, 
        type = 'pie',
        marker = list(colors = hana_color_palette(n_distinct(meet_data_detail$member_product),2),
                      line = list(color = '#FFFFFF', width = 1))) %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
})

```

Meet Resources
===================================== 

Column {data-width=600}
-------------------------------------

### Reservations by Room

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>% 
    group_by(name) %>% 
    summarise(bookings=n()) %>% 
    arrange(bookings) %>% 
    mutate(name=forcats::as_factor(as.character(name))) %>%
    plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~name,
          x = ~bookings,
          bargroupgap=0.1,
          bargap = 0.15,
          type="bar")
})   



```

Column {data-width=200}
-------------------------------------

### Reservations Lead Time by Reservation Length

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>% 
    filter(meeting_length<=1000,
         booking_lead_time<=1000) 
  
  meet_data_detail %>% 
    plot_ly(x = ~jitter(as.numeric(meeting_length)), 
          y = ~booking_lead_time,
          color = ~member_product, 
          colors = hana_color_palette(n_distinct(meet_data_detail$hana_location),2))
})
```



Column {data-width=200}
-------------------------------------

### Reservations by Room Capacity

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>% 
    group_by(max_density) %>% 
    summarise(bookings=n()) %>% 
    arrange(bookings) %>% 
#    mutate(max_density=forcats::as_factor(as.character(max_density))) %>%
    plot_ly(marker = list(color = "#002D36"),
          orientation='v',
          y = ~bookings,
          x = ~max_density,
          bargroupgap=0.1,
          bargap = 0.15,
          type="bar")
})

```

### Reservations by Seating Type

```{r }

renderPlotly({
  meet_data_detail<-updatedMeetData() %>% 
    group_by(seating_type) %>% 
    summarise(bookings=n()) %>% 
    arrange(bookings) %>% 
    mutate(seating_type=forcats::as_factor(as.character(seating_type))) %>%
    plot_ly(marker = list(color = "#002D36"),
          orientation='h',
          y = ~seating_type,
          x = ~bookings,
          bargroupgap=0.1,
          bargap = 0.15,
          type="bar")
})

```


Meet Detail
===================================== 

```{r }


DT::renderDataTable({
datatable(updatedMeetData(), escape = FALSE,rownames = FALSE, extensions = c('Scroller', 'Buttons'), 
          options = c(list(scrollY = 800, scroller = TRUE, scrollX=TRUE, deferRender=TRUE, dom = 'fBrtip',buttons = c('csv'))))
})
```

